Algorithms for Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2015-04-25 paper/paper.tex

\section*{Acknowledgments}
This work was supported by the U.S. Department of Energy Office of Science
under award number ER26110, by the National Science Foundation ACI SI2-SSI
program award number 1148515, and by the EU FP7 project VPH-Share (269978).

>>>>

\section*{Acknowledgments}
This work was supported by the U.S. Department of Energy Office of Science
under award number ER26110, by the National Science Foundation ACI SI2-SSI
program award number 1148515, by the AGH grant 11.11.230.124 
and by the EU FP7 project VPH-Share (269978).
